Titeln på avhandlingens språk

### 2022-09-24 publications/2018DemoScalingOnTheEdge/paper_body.tex
starting to include papers
fixing references

Previous works on cloudlets~\cite{satya2009case,Ha:ImpactMobile}, one of the earliest incarnation of edge computing, enable small data-centers at the edge of the Internet. 
Many futuristic applications become viable with these clusters that are only one wireless hop away. 
One of the most promising genres of these emerging applications is human-in-the-loop applications such as wearable cognitive assistance~\cite{Ha:TowardsWearableCogAssist}.

In these applications, sensor data, for example video and audio, are continuously streamed to a cloudlet, where they are analyzed in realtime in order to assist users to complete a particular task. 
Researchers have built prototypes of these applications to help users assemble LEGO models and IKEA furniture, and even learn how to play ping-pong~\cite{satya2009case,Chen:EarlyImplementation}.
% In general, all human-in-the-loop applications capture in some form user and environment information and typically leverage compute-intensive algorithms to analyze the data in order to provide feedback to the user.
% On the side of the sensory input, typically video, but also audio as well as further user-related data (like orientation and movement) is captured.
% This  data is forwarded to the processing unit where the first step is usually to run detection algorithms on the sensory input.
% In case of a positive result from the detection, the next step is then the generation of feedback to be sent back to the user.

@@

\begin{description}[labelindent=\parindent, listparindent=\parindent, style=unboxed, leftmargin=0cm]
	\item[Latency Sensitive:] Given their tight interaction with the physical world, the quality of human-in-the-loop applications is determined by the latencies experienced by users. 
    These applications are different from conventional mobile applications by the low latency requirements inherent to the applications themselves~\cite{Suzuki,Chen:AnEmpiricalStudyOfLatency}. 
    For example, consider a Ping-Pong Assistance application that instructs a user where to hit a ball -- any instruction delivered after the user has made a hit is useless.
  Hence, the average and the distribution of end-to-end latency, in particular for \emph{feedback-rich} inputs, can serve as good metrics for a benchmark tool. 
% Previous work has shown that offload to cloudlet reduces 100ms to 200ms in end-to-end latency from offload to the cloud \cite{Suzuki,Chen:AnEmpiricalStudyOfLatency}.
% Thus, the low latency benefits provided by cloudlets distinguish human-in-the-loop applications from conventional mobile or web applications. 
% Therefore, low latency is a salient characteristic of cloudlet-enabled applications.

    \item[Compute Intensive:] Cognitive Assistance applications aim to enhance the cognitive capabilities of users, and are thus compute intensive as well due to widespread use of the state-of-art computer vision and machine learning algorithms, particularly Deep Neural Networks (DNNs). 
    Although mobile devices are becoming increasingly powerful, the gap between mobile and static elements continues to exist~\cite{flinn2012cyber}. 
    While state-of-the-art DNN object detectors can run at more than 20 FPS on a server GPU, their performances are much worse on mobile GPUs - some models cannot even be loaded due to memory constraints. 
    Cloudlet-based applications overcome these challenges by offloading the computation. 
%    Offloading makes sense when the computation is intensive or special hardwares are needed.

@@

\begin{description}[labelindent=\parindent, listparindent=\parindent, style=unboxed, leftmargin=0cm]
  \item [The application backend] consists of instances of the target application running on \textcite{docker} containers. 
  These correspond to real, unaltered instances of said cognitive assistance applications -- we do not model or emulate them in any way -- and they are containerized in order to be able to execute an arbitrary number of them on the same cloudlet.
  \item [The client emulator] consists of an Android application which emulates the behavior of a user operating the target cognitive assistance application while following the previously discussed user model.
  This Android app replays the previously recorded sensory data over the network to a specific \emph{application backend}, while collecting statistics and measurements of the system status. 
  %{\color{blue} Junjue: Should there be an application client in the picture? Logically, the benchmark android app feeds the application client the sensory information it needs, almost like hijacking the camera stream.}
  \item [The control backend] also runs on the cloudlet, although it could be executed in a separate cloud or cloudlet. It controls the execution of the experiments, by controlling the \emph{client emulators} over the network, initializing the \emph{application backends} and finally aggregating collected data when the experiments are completed. 
\end{description}

\begin{figure}
  \centering
  \includegraphics[width=.7\columnwidth]{img/TraceReplay_GenArch}
  \captionof{figure}{General architecture of the benchmarking suite.}
  \label{fig:TraceReplayArch}
\end{figure}

@@

We will demonstrate the benchmarking framework using the \emph{LEGO Task Guidance} application previously developed by \textcite{Chen:EarlyImplementation}.
This application guides a user step by step in the assembly of a LEGO model; input consists exclusively of video feed of the current state of the assembly, whereas feedback includes visual and auditory components in the form of animations and speech, respectively.

The benchmarking tool will be employed to extract key real-time metrics from this application, \emph{e.g.} average computation and network times, as well as the estimated \emph{user experience} level of the system as a whole (\emph{flawless}, \emph{impaired} or \emph{unusable}, based on the categorization in \cite{Chen:AnEmpiricalStudyOfLatency}).

>>>>

Previous works on cloudlets~\cite{Satya2009Case,Ha2013Impact}, one of the earliest incarnation of edge computing, enable small data-centers at the edge of the Internet. 
Many futuristic applications become viable with these clusters that are only one wireless hop away. 
One of the most promising genres of these emerging applications is human-in-the-loop applications such as wearable cognitive assistance~\cite{Ha2014Towards}.

In these applications, sensor data, for example video and audio, are continuously streamed to a cloudlet, where they are analyzed in realtime in order to assist users to complete a particular task. 
Researchers have built prototypes of these applications to help users assemble LEGO models and IKEA furniture, and even learn how to play ping-pong~\cite{Satya2009Case,Chen2015Early}.
% In general, all human-in-the-loop applications capture in some form user and environment information and typically leverage compute-intensive algorithms to analyze the data in order to provide feedback to the user.
% On the side of the sensory input, typically video, but also audio as well as further user-related data (like orientation and movement) is captured.
% This  data is forwarded to the processing unit where the first step is usually to run detection algorithms on the sensory input.
% In case of a positive result from the detection, the next step is then the generation of feedback to be sent back to the user.

@@

\begin{description}[labelindent=\parindent, listparindent=\parindent, style=unboxed, leftmargin=0cm]
	\item[Latency Sensitive:] Given their tight interaction with the physical world, the quality of human-in-the-loop applications is determined by the latencies experienced by users. 
    These applications are different from conventional mobile applications by the low latency requirements inherent to the applications themselves~\cite{Suzuki2016Vehicle,Chen2017Empirical}. 
    For example, consider a Ping-Pong Assistance application that instructs a user where to hit a ball -- any instruction delivered after the user has made a hit is useless.
  Hence, the average and the distribution of end-to-end latency, in particular for \emph{feedback-rich} inputs, can serve as good metrics for a benchmark tool. 
% Previous work has shown that offload to cloudlet reduces 100ms to 200ms in end-to-end latency from offload to the cloud \cite{Suzuki,Chen:AnEmpiricalStudyOfLatency}.
% Thus, the low latency benefits provided by cloudlets distinguish human-in-the-loop applications from conventional mobile or web applications. 
% Therefore, low latency is a salient characteristic of cloudlet-enabled applications.

    \item[Compute Intensive:] Cognitive Assistance applications aim to enhance the cognitive capabilities of users, and are thus compute intensive as well due to widespread use of the state-of-art computer vision and machine learning algorithms, particularly Deep Neural Networks (DNNs). 
    Although mobile devices are becoming increasingly powerful, the gap between mobile and static elements continues to exist~\cite{Flinn2012Cyber}. 
    While state-of-the-art DNN object detectors can run at more than 20 FPS on a server GPU, their performances are much worse on mobile GPUs - some models cannot even be loaded due to memory constraints. 
    Cloudlet-based applications overcome these challenges by offloading the computation. 
%    Offloading makes sense when the computation is intensive or special hardwares are needed.

@@

\begin{description}[labelindent=\parindent, listparindent=\parindent, style=unboxed, leftmargin=0cm]
  \item [The application backend] consists of instances of the target application running on Docker containers. 
  These correspond to real, unaltered instances of said cognitive assistance applications -- we do not model or emulate them in any way -- and they are containerized in order to be able to execute an arbitrary number of them on the same cloudlet.
  \item [The client emulator] consists of an Android application which emulates the behavior of a user operating the target cognitive assistance application while following the previously discussed user model.
  This Android app replays the previously recorded sensory data over the network to a specific \emph{application backend}, while collecting statistics and measurements of the system status. 
  %{\color{blue} Junjue: Should there be an application client in the picture? Logically, the benchmark android app feeds the application client the sensory information it needs, almost like hijacking the camera stream.}
  \item [The control backend] also runs on the cloudlet, although it could be executed in a separate cloud or cloudlet. It controls the execution of the experiments, by controlling the \emph{client emulators} over the network, initializing the \emph{application backends} and finally aggregating collected data when the experiments are completed. 
\end{description}

\begin{figure}
  \centering
  \includegraphics[width=.7\columnwidth]{publications/2018DemoScalingOnTheEdge/img/TraceReplay_GenArch}
  \captionof{figure}{General architecture of the benchmarking suite.}
  \label{fig:TraceReplayArch}
\end{figure}

@@

We will demonstrate the benchmarking framework using the \emph{LEGO Task Guidance} application previously developed by \textcite{Chen2015Early}.
This application guides a user step by step in the assembly of a LEGO model; input consists exclusively of video feed of the current state of the assembly, whereas feedback includes visual and auditory components in the form of animations and speech, respectively.

The benchmarking tool will be employed to extract key real-time metrics from this application, \emph{e.g.} average computation and network times, as well as the estimated \emph{user experience} level of the system as a whole (\emph{flawless}, \emph{impaired} or \emph{unusable}, based on the categorization in \cite{Chen2017Empirical}).
